\documentclass[10pt]{article}

\begin{document}
\title{Use Cases}
\maketitle

\section*{Team Members}
\begin{itemize}
\item Lovedeep Singh - C0748774
\item Khaleel Khan - C0749217
\item Goldy Verma - C0749947
\item Aanchal Devi - C0748160
\item Gaganpreet Kaur - C0747813
\end{itemize}

\section{Use Case for R1: To create the Statement of Work  }
\subsection{Use Case Name/Goal: To enable the User  to write their SOW using this software applictaion}
This is to provide the user a screen with an input panel so that the user can write a Statement of work for project.

\subsection{ACTOR: The Project Manager(User)}

\subsection{SCENARIO: }

\begin{itemize}
  \item Step 1: The User Activates the Screen in the Software for the Create SOW function.
  \item Step 2: The user is prompted to type in a detailed description of their work requirements.
  \item Step 3: The user is has a BUTTON to save and exit their work when done. When they exit, the SOW is persisted to data storage.
\end{itemize}




\section{Use Case for R2: To create the Work Breakdown Structure  }

\subsection{Use Case Name/Goal: Give the User a SCREEN or UI to create their SOW}
The goal of this Use Case is to provide user enough access to breakdown the whole project into smaller tasks so that it gets easier to complete the project.
\subsection{ PRECONDITION:}
 Statement of work is needed to create a work breakdown structure.
\subsection{ACTORS:}
\begin{itemize}
  \item   The Project Manager(User)
  \item  The Data Storage(which gets updated)
 \item The coordinators who will document the project

\end{itemize}
						

\subsection{SCENARIO: }

\begin{itemize}
  \item Step 1: The User Activates the Screen in the Software for the Create SOW function.
  \item Step 2: The user enters required authentication id and password to log in.
  \item Step 3: The user goes to the main menu and selects the Item for Creating Work Breakdown Structure.
\item  Step 4: The user creates the WBS with0 DETAILED information including the instructions for the team members to convert the project requirements into actionable activities.
\item Step 5: The user keeps decomposing the tasks into SUBTASKS until they arrive a task that can be easily done within one day as the user have function to decompose the TASKS.
\item Step 6: the user saves the WBS and updates into DATABASE STORAGE and exits the application. 
\end{itemize}

\section{Use Case for R3: TO create the resource register  }

\subsection{Use Case Name/Goal: }
To enable the project manager to create a List of available project resources such as Team members with skills

\subsection{ACTORS:}
\begin{itemize}
  \item   The Project Manager(User)
  \item  The Data Storage(which gets updated)
 \item The coordinators who will document the project
\item The HR Manager


\end{itemize}
						

\subsection{SCENARIO: }

\begin{itemize}
  \item Step 1: The User Activates the Screen in the Software for the Create SOW function.
  \item Step 2: The user enters required authentication id and password to log in.
  \item Step 3: The user goes to the main menu and selects the Menu Item for Create /Modify Resource Register.
\item  Step 4: The User creates/modifies/deletes RESOURCES including Team members' profiles and other information.
\item Step 5:  The User saves the Resouce register and exits the application.
\end{itemize}

\end{document}


